The shape of dark matter halos in the AURIGA simulations

### 2019-02-20 Paper/paper.tex
edit

This average behaviour of more round halos in MHD can be seen more
clearly in the individual case of Halo 16, shown in Figure
\ref{fig:triaxial_radius}.  
At the virial radius the halo is rounder than its DM counterpart. 
Going from the virial radius to $10$ \kpch the $b/a$ ratio is constant almost close to unity
in the MHD simulation while it decreases to $0.5$ in DM-only
simulation. 
Between $2$-$10$ \kpc the triaxiality in the DM-only simulation is in
the range $0.9-1.0$, while the MHD simulation has values between
$0-0.5$.

In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
we summarize these trends for the median values of the axis ratio in
the two sets of simulations (DM and MHD). 
The lower/upper bounds correspond to the first/third quartiles. 
Summarizing: a) Table  \ref{table:median_axial_ratio_DM} shows how halos are
monotonically rounder with increasing radius; b) the comparison
against Table \ref{table:median_axial_ratio_MHD} shows  how DM halos
are consistently rounder in MHD simulations than DM-only runs at every radius.

>>>>

This global behaviour can be also illustrated by the individual case
of Halo 16, shown in Figure \ref{fig:triaxial_radius}.
At the virial radius the halo is rounder than its DM counterpart as
evidenced in the axis ratios $b/a$, $c/a$ and the triaxiality.
In the MHD simulation, going from the virial radius to $10$ \kpch the
$b/a$ ratio is constant almost close to unity while in the DM-only
simulation it decreases to $0.5$.
Between $2$-$10$ \kpc the triaxiality in the DM-only simulation is in
the range $0.9-1.0$, while the MHD simulation has values between
$0-0.5$.

In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
we summarize these trends for the median values of the axis ratio in
the DM and MHD simulations
The lower/upper bounds correspond to the first/third quartiles. 
Table  \ref{table:median_axial_ratio_DM} shows how halos are
monotonically rounder with increasing radius; while the comparison
against Table \ref{table:median_axial_ratio_MHD} shows how DM halos
are consistently rounder in MHD simulations than DM-only runs at every
radius.
